---
title: "`r paste('Consumer Confidence Report for PWS: ', params$psid)`"
subtitle: "`r paste0(params$nam, ', ', params$city, ' (', params$county, ' CO.)')`"
date: "`r paste0('For the period from ', paste0(lubridate::year(Sys.Date()) - 2, '-01-01'), ' to ', Sys.Date(), '.')`"
output: 
  html_document:
    #theme: default
    toc: true
    toc_float: true
params: 
  psid: 0001
  nam: "aaa"
  city: "aaa"
  county: "aaa"
---


```{r, echo=FALSE}
library(knitr)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(tidyverse)
library(lubridate)
library(tibbletime)
library(forcats)
library(plotly)
library(DT)
library(mapview)
library(sf)

# minimal data (~4 GB)
#d <- read_rds("/Users/richpauloo/Desktop/ca_water_datathon/chem_tp_min.rds")
d <- filter(chem_tp_min_2017, PRIM_STA_C == params$psid)

# address/contact data
cd <- filter(psid_contact, PRIM_STA_C == params$psid)

# vars to report
wst <- formatC(d$`Primary Water Source Type`[1], big.mark = ",")
tsc <- formatC(d$`Total Number of Service Connections`[1], big.mark = ",")
pop <- formatC(d$`Total Population`[1], big.mark = ",")

# map: in order for this to work, `04_generate_ccrs.R` needs to read in
# sa as a sf object, so that it's subsettable by `dplyr::filter()`
# my_water_system <- filter(sa, pwsid == params$psid)
my_water_system <- filter(st_as_sf(ep), WATER_SYST == params$psid) %>% 
  select(-c(url, DEFAULT_ME, ObjectID)) %>% 
  rename(WATER_SYSTEM_NUMBER = WATER_SYST,
         WATER_SYSTEM_NAME = WATER_SY_1,
         REGULATING_AGENCY = REGULATING,
         CLASSIFICATION = CLASSIFICA,
         CITY = CITY_1,
         VIOLATION_DETAILS = DETAILED_V,
         SERVICE_CONNECTIONS = Service_Co)


# text for water quality plot
l1a <- "Of the "
l1b <- " chemicals tested for in your water system, "
l1c <- " **chemicals were detected**, and " 
l1d <- " **average annual chemical findings exceeded their MCL, though this dos not necessarily constitute an MCL violation [$^*$](#vio-link)**. <br>"
l2 <- "In the plot below, the Maximum Contaminant Level (MCL) is shown as a black horizontal dashed line. Each contaminant tested for in your water utility is represented by a vertical bar, and the height of the bar indicates the level of contaminantion of that sample. Any contaminant at or exceeding the black horizontal dashed line indicates contaminated water, and values under the black line indicate **safe** drinking water. <br><br> Hover over the bars to see more information for each contaminant."


# text for psids with detects and non-detects
l3 <- " **other chemicals were tested for and NOT detected**, including: <br><br> "
l4 <- " <br><br> Because they were not detected, these chemicals are not included in the chart above."

# text for psids with no records of detects
l5 <- "**Although tests were made, no chemicals were detected in your water system.**" 
l6 <- "The following chemicals were tested for: "

l6a <- "The following **" 
l6b <- "** water quality indicators were tested for in your system and, may have been detected (see the [table below](#table)), though they pose no serious human health hazard, and hence have an MCL of 0: "  

# exceedance note - deprecated
# l7 <- "If a contaminant has an exceedance of 999%, this indicates a detection for which the MCL is 0. Any number divided by 0 is infinite, thus it is assigned an arbitarty large value (999) to indicate exceedance." 


# plotly buttons to remove
buttons_to_remove <- list("zoom2d", "select2d", "lasso2d", "autoscale",
                          "hoverClosestCartesian", "hoverCompareCartesian",
                          "zoom3d", "pan3d", "resetCameraDefault3d", "resetCameraLastSave3d", "hoverClosest3d",
                          "orbitRotation", "tableRotation",
                          "zoomInGeo", "zoomOutGeo", "resetGeo", "hoverClosestGeo",
                          "sendDataToCloud",
                          "hoverClosestGl2d",
                          "hoverClosestPie",
                          "toggleHover",
                          "toggleSpikelines", "pan")
```


```{r}
# calculate average annual finding per chemical
# and the proportion exceedance of the MCL
dg <- d %>% 
  filter(CHEMICAL__ != "PH, LABORATORY") %>%
  group_by(CHEMICAL__, MCL, RPT_UNIT, XMOD) %>% 
  summarise(mean_finding = mean(FINDING)) %>% 
  ungroup() %>% 
  mutate(prop_mcl = abs((mean_finding/MCL))*100,
         # valid measurements are blank (NA) in the data, so encode them
         XMOD     = ifelse(is.na(XMOD), "V", XMOD))#, 
         # MCL of 0 cause Inf results, encode as 999
         #prop_mcl = ifelse(is.infinite(prop_mcl), 999, prop_mcl))

# water quality indicators
wqi <- filter(dg, MCL == 0)

# contaminants
dg <- filter(dg, MCL != 0)

# chemical is detected
dg1 <- filter(dg, prop_mcl > 0 & XMOD != "<")  

# chemical not detected
dg2 <- filter(dg, XMOD == "<" | mean_finding == 0 ) 

# exceedance events
ee <- nrow(filter(dg1, prop_mcl >= 100))

# violation status
vio <- filter(ep@data, WATER_SYST == params$psid) %>% pull(GIS_STATUS)
viostr <- paste0(" This water system is **", vio, "**")  
if(length(vio) == 1){
  if(vio == "RETURNED TO COMPLIANCE"){
    viostr <- paste0(" This water system has **", vio, "**")
  }
}
if(length(vio)==0) {viostr <- " Compliance status is **UNKNOWN** for this water system"}
contactstr <- '[Contact your water system](#contact-link) for more information.'

if(length(vio) == 1){ 
  if(vio == "IN COMPLIANCE") viostr <- paste0(" ", fontawesome::fa("check-circle", fill = "green"), viostr)
  if(vio == "OUT-OF-COMPLIANCE") viostr <- paste0(" ", fontawesome::fa("exclamation-circle", fill = "red"), viostr)
  if(vio == "RETURNED TO COMPLIANCE") viostr <- paste0(" ", fontawesome::fa("check-circle", fill = "green"), viostr)
}
if(length(vio) == 0){
  viostr <- paste0(" ", fontawesome::fa("question-circle", fill = "red"), viostr)
}
```


***  


## What does this report mean? 

`r paste0('Drinking water quality in your water system is tested for many chemical constituents as required by state and federal regulations. This report shows monitoring results for the period from ', paste0(lubridate::year(Sys.Date()), '-01-01'), ' to ', Sys.Date(), '.')`

<!-- * more lay interpretation for people and how it applies to user. Scope language is in [this template](https://www.waterboards.ca.gov/drinking_water/certlic/drinkingwater/documents/ccr/3ccr_swsrpttemplate_for_2018_ccr_english_20190219.docx).  -->


Este informe contiene información muy importante sobre su agua para beber. Favor de comunicarse `r params$nam` a [`r cd$WS_PHONE`](#contact-link) para asistirlo en español.

这份报告含有关于您的饮用水的重要讯息。请用以下地址和电话联系 `r params$nam` 以获得中文的帮助: [`r cd$WS_PHONE`](#contact-link). 


***

## `r viostr`

**`r params$nam`** is located in **`r paste0(params$city, ' (', params$county, ' CO.)')`**. 

The primary water source type is **`r wst`**. 

This water system services **`r tsc`** connections, and serves a total population of **`r pop`** individuals.

```{r, out.width="100%"}
if(nrow(my_water_system) > 0 ){
  mapview(my_water_system, legend = FALSE)
}
```



***  


<!-- ## How clean is my water?  -->


## Chemicals detected

`r if(length(vio) == 0) contactstr`

`r if(nrow(dg1) > 0) paste0(l1a, "**", nrow(dg), "**", l1b, "**", nrow(dg1), "**", l1c, "**", ee, "**", l1d) `

`r if(nrow(dg1) > 0) paste(l2) `



```{r, out.width="100%"}
colourCount = length(unique(dg1$CHEMICAL__))
getPalette = colorRampPalette(RColorBrewer::brewer.pal(9, "Set1"))

if(nrow(dg1) > 0){
  p <- mutate(dg1, CHEMICAL__ = stringr::str_wrap(CHEMICAL__, 15,1,1)) %>% 
    ggplot(aes(fct_reorder(CHEMICAL__, prop_mcl), 
                       prop_mcl, 
                       fill = CHEMICAL__,
                       text = paste("Chemical:", CHEMICAL__, "<br>",
                                    "Exceedance:", round(prop_mcl, 2), "%", "<br>",
                                    "Average Result:", round(mean_finding, 2), RPT_UNIT, "<br>",
                                    "MCL:", MCL, RPT_UNIT, "<br>",
                                    "XMOD:", XMOD),
                       group = 1)) +
    geom_col() +
    scale_y_continuous(breaks = c(0,25,50,75,100),
                       labels = function(x) paste0(x, "%")) +
    coord_cartesian(ylim = c(0, 110)) +
    labs(x = "Chemical", y = "Percent MCL Exceedance (%)", fill = "% Exceedance",
         #title = "How Clean is my Water?",
         subtitle = "Values less than 100% are safe.") +
    geom_hline(yintercept = 100, linetype = "dashed", color = "black") +
    #annotate("text", x = nrow(dg1)/3, y = 90, angle = 90, color = "red",
    #         label = "MCL Threshold") + 
    #coord_flip() +
    #scale_fill_viridis_d() +
    #scale_fill_brewer(palette = "Set2") +
    scale_fill_manual(values = getPalette(colourCount)) + 
    theme_minimal() +
    theme(panel.grid.minor = element_blank(),
          axis.text.x = element_blank(),
          panel.grid.major.x = element_blank()) +
    guides(fill = FALSE)
  
  ggplotly(p, tooltip = "text") %>% 
    config(modeBarButtonsToRemove = buttons_to_remove,
           displaylogo = FALSE)
}
```

`r if(nrow(dg1) > 0 & nrow(dg2) > 0) paste0("**", nrow(dg2), "**", l3, paste(dg2$CHEMICAL__, collapse = ", "), "." , l4) `

`r if(nrow(dg1) == 0 & nrow(dg2) > 0) paste0(l5, "<br><br>", l6, paste(dg2$CHEMICAL__, collapse = ", "), ".") `

`r if(nrow(wqi) > 0) paste0(l6a, nrow(wqi), l6b, "<br><br>", paste(wqi$CHEMICAL__, collapse = ", "), ".")`



***  


## Actions taken to address MCL exceedances _[in progress]_ 
<!-- ## r if(nrow(violations) > 0) paste('Actions taken to assess violations') -->

When a measured contaminant exceeds the MCL, a set of regulatory actions is taken to improve water quality. All regulatory actions taken during the period of this report are shown below:  

Table or text summarizing this.  



***  



## Explore/download data {#table}

Explore your water quality data in the interactive table below, or download as an Excel or CSV file.  

```{r}
dg %>% 
  select(CHEMICAL__, mean_finding, MCL, RPT_UNIT, XMOD) %>% 
  mutate(mean_finding = round(mean_finding, 2)) %>% 
  datatable(., 
            colnames = c("CHEMICAL", "SAMPLE_MEAN","MCL","UNIT", "XMOD"),
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('excel', "csv")))
```

*** 

<!-- ## How does my water compare to county and statewide averages? -->


<!-- ***   -->


<!-- ## My water quality over time. -->

<!-- Only showing this year's water quality data. What about the past 5 years? -->

<!-- ***   -->



## More information

### *Contact Water System* {#contact-link}

##### `r params$nam`  
`r paste0(" ", fontawesome::fa("map-marker", fill = "red"), " : ", cd$WS_ADDRESS)`  
`r paste0(" ", fontawesome::fa("phone", fill = "blue"), ": ", cd$WS_PHONE)`  

### *Contact Health System*

##### `r cd$HEALTH_DISTRICT`

`r paste0(" ", fontawesome::fa("map-marker", fill = "red"), " : ", cd$HD_ADDRESS)`  
`r paste0(" ", fontawesome::fa("phone", fill = "blue"), ": ", cd$HD_PHONE)`  
`r paste0(" ", fontawesome::fa("paper-plane", fill = "green"), ": ", cd$HD_EMAIL)` 

### Disclaimer

This Consumer Confidence Report was automatically generated, and hence, the data herein may be incomplete or inaccurate. The authors claim no liability or responsibility for data quality. This data represents the average result of all post-treatment samples from the period from `r paste0(paste0(lubridate::year(Sys.Date()), '-01-01'), ' to ', Sys.Date())`. For questions about your local water quality, contact your water system.  


### Frequently Asked Questions {#vio-link}

#### *Important Vocabulary*

* **Maximum Contaminant Level (MCL)** refers to the highest level of a contaminant that is allowed in drinking water.  Primary MCLs are set as close to the PHGs (or MCLGs) as is economically and technologically feasible. Secondary MCLs are set to protect the odor, taste, and appearance of drinking water.  

* **In Compliance**: If a water system is "In Compliance" it means that the system is achieving compliance with the federal/state primary drinking water standards (i.e. MCL and TT requirements). For chronic contaminants, compliance is defined based on the running annual average (RAA), as specified in Section 64432 of Title 22 of the California Code of Regulations (CCR). For nitrate, compliance is based on quarterly monitoring as specified in Section 64432.1 of Title 22 of the CCR. To find out more about the types of contaminants and their associated MCLs, refer to the table of [Maximum Contaminant Levels and Regulatory Dates for Drinking Water](http://www.waterboards.ca.gov/drinking_water/certlic/drinkingwater/documents/dwdocuments/MCLsEPAvsDWP-2014-07-01.pdf).  

There are certain state drinking water standards, such as perchlorate, which are more stringent than the federal drinking water standards.  

* **Out of Compliance**: If a water system is "Out-of-Compliance" it means that the system is currently in violation of one or more federal/state primary drinking water standard (i.e. MCL and TT requirements) and an enforcement action has been taken.  

* **Returned to Compliance**: If a water system has returned to compliance since January 1, 2012 it means the water system now meets federal/state primary drinking water standards (i.e. MCL and TT requirements), but did not in the recent past.  


#### *Explanation of terms in this report*

In the barplot and table above, `XMOD` indicates additional qualifiers on the data.  

* `<`: the measured amount did not constitute a chemical detection  
* `V`: valid data  
* `-`: the data can be negative (e.g. radionuclides and Langelier index)  
* `F`: false positive  
* `I`: invalidated  
* `Q`: questionable 



