---
title: "`r paste(params$nam, ' Consumer Confidence Report')`"
subtitle: "`r paste0('PSID: ', params$psid, '  |  ', params$city, ', ', params$county, ' CO.')`"
date: "`r paste0('For the period from ', paste0('2017-01-01 to ', Sys.Date(), '.'))`"
output: 
  html_document:
    toc: true
    toc_float: true
params: 
  psid: 0001
  nam: "aaa"
  city: "aaa"
  county: "aaa"
---

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #414141;
}
</style>

```{r, echo=FALSE}
library(knitr)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(tidyverse)
library(lubridate)
library(tibbletime)
library(forcats)
library(plotly)
library(DT)
library(mapview)
library(sf)

# minimal data (~4 GB)
#d <- read_rds("/Users/richpauloo/Desktop/ca_water_datathon/chem_tp_min.rds")
d <- filter(chem_tp_min_2017, PRIM_STA_C == params$psid)

# address/contact data
cd <- filter(psid_contact, PRIM_STA_C == params$psid)

# vars to report
wst <- formatC(d$`Primary Water Source Type`[1], big.mark = ",")
tsc <- formatC(pull(filter(ep@data, WATER_SYST == params$psid), Service_Co)[1], 
               big.mark = ",", format = "d")
pop <- formatC(as.numeric(pull(filter(ep@data, WATER_SYST == params$psid), POPULATION)[1]), 
               big.mark = ",", format = "d")

# map: in order for this to work, `04_generate_ccrs.R` needs to read in
# sa as a sf object, so that it's subsettable by `dplyr::filter()`
# my_water_system <- filter(sa, pwsid == params$psid)
my_water_system <- filter(st_as_sf(ep), WATER_SYST == params$psid) %>% 
  select(-c(url, DEFAULT_ME, ObjectID)) %>% 
  rename(WATER_SYSTEM_NUMBER = WATER_SYST,
         WATER_SYSTEM_NAME = WATER_SY_1,
         REGULATING_AGENCY = REGULATING,
         CLASSIFICATION = CLASSIFICA,
         CITY = CITY_1,
         VIOLATION_DETAILS = DETAILED_V,
         SERVICE_CONNECTIONS = Service_Co)


# text for water quality plot
l1a <- "Of the "
l1b <- " chemicals tested for in your water system, "
l1c <- " **chemicals were detected**, and " 
l1d <- " **average chemical findings exceeded their MCL, though exceedance alone does not constitute a violation [$^*$](#vio-link)**. <br>"
l2 <- "In the plot below, the Maximum Contaminant Level (MCL) is shown as a black horizontal dashed line. Each vertical bar is a contaminant that was detected. The higher the bar, the higher the average level of that contaminant over the period of record. Any contaminant at or above the black horizontal dashed line indicates contaminated water. <br><br> Hover over the bars to see more information."


# text for psids with detects and non-detects
l3 <- " **other chemicals were tested for and NOT detected**, including: <br><br> "
l4 <- " <br><br> Because they were not detected they are not included in the chart above."

# text for psids with no records of detects
l5 <- "**Although tests were made, no chemicals were detected in your water system.**" 
l6 <- "The following chemicals were tested for: "

l6a <- "The following **" 
l6b <- "** water quality indicators were tested for in your system and, may have been detected (see the [table below](#table)), though they pose no serious human health hazard, and hence have an MCL of 0: "  

# exceedance note - deprecated
# l7 <- "If a contaminant has an exceedance of 999%, this indicates a detection for which the MCL is 0. Any number divided by 0 is infinite, thus it is assigned an arbitarty large value (999) to indicate exceedance." 

# new line that removes unnecessary text vom of all chemical nondetects.
l7 <- " other chemicals were tested for and NOT detected. They are not included in the chart above, but are reported in the table [below](#table)."
l8 <- "** water quality indicators were tested for and may have been detected, though they pose no serious human health hazard (MCL = 0). They are reported in the [table below](#table)."


# plotly buttons to remove
buttons_to_remove <- list("zoom2d", "select2d", "lasso2d", "autoscale",
                          "hoverClosestCartesian", "hoverCompareCartesian",
                          "zoom3d", "pan3d", "resetCameraDefault3d", "resetCameraLastSave3d", "hoverClosest3d",
                          "orbitRotation", "tableRotation",
                          "zoomInGeo", "zoomOutGeo", "resetGeo", "hoverClosestGeo",
                          "sendDataToCloud",
                          "hoverClosestGl2d",
                          "hoverClosestPie",
                          "toggleHover",
                          "toggleSpikelines", "pan")
```


```{r}
# calculate average annual finding per chemical
# and the proportion exceedance of the MCL
dg <- d %>% 
  filter(CHEMICAL__ != "PH, LABORATORY") %>%
  group_by(CHEMICAL__, MCL, RPT_UNIT, XMOD) %>% 
  summarise(mean_finding = mean(FINDING)) %>% 
  ungroup() %>% 
  mutate(prop_mcl = abs((mean_finding/MCL))*100,
         # valid measurements are blank (NA) in the data, so encode them
         XMOD     = ifelse(is.na(XMOD), "V", XMOD))#, 
         # MCL of 0 cause Inf results, encode as 999
         #prop_mcl = ifelse(is.infinite(prop_mcl), 999, prop_mcl))

# water quality indicators
wqi <- filter(dg, MCL == 0)

# contaminants
dg <- filter(dg, MCL != 0)

# chemical is detected
dg1 <- filter(dg, prop_mcl > 0 & XMOD != "<")  

# chemical not detected
dg2 <- filter(dg, XMOD == "<" | mean_finding == 0 ) 

# exceedance events
ee <- nrow(filter(dg1, prop_mcl >= 100))

# violation status
vio <- filter(ep@data, WATER_SYST == params$psid) %>% pull(GIS_STATUS)

if(length(vio) == 1){
  if(vio == "RETURNED TO COMPLIANCE"){
    viostr <- paste0(" Status: **", vio, "**")
  }
}

if(length(vio) == 0){ 
  viostr <- " Compliance status is **UNKNOWN** for this water system"
}

contactstr <- '[Contact your water system](#contact-link) for more information.'

if(length(vio) == 1){ 
  if(vio == "IN COMPLIANCE") 
    viostr <- paste0(" ", fontawesome::fa("check-circle", fill = "green"), 
                     paste0(" Status: **<font color = 'green'>", vio, "</font>**") )
  if(vio == "OUT-OF-COMPLIANCE") 
    viostr <- paste0(" ", fontawesome::fa("exclamation-circle", fill = "red"), 
                     paste0(" Status: **<font color = 'red'>", vio, "</font>**") )
  if(vio == "RETURNED TO COMPLIANCE") 
    viostr <- paste0(" ", fontawesome::fa("check-circle", fill = "orange"), 
                     paste0(" Status: **<font color = 'orange'>", vio, "</font>**") )
}

if(length(vio) == 0){
  viostr <- paste0(" ", fontawesome::fa("question-circle", fill = "red"), viostr)
}
```


***  


## What does this report mean? 

This report contains important information about drinking water quality in your water system.  

<!-- * more lay interpretation for people and how it applies to user. Scope language is in [this template](https://www.waterboards.ca.gov/drinking_water/certlic/drinkingwater/documents/ccr/3ccr_swsrpttemplate_for_2018_ccr_english_20190219.docx).  -->


Este informe contiene información muy importante sobre su agua para beber. Favor de comunicarse `r params$nam` a [`r cd$WS_PHONE`](#contact-link) para asistirlo en español.

这份报告含有关于您的饮用水的重要讯息。请用以下地址和电话联系 `r params$nam` 以获得中文的帮助: [`r cd$WS_PHONE`](#contact-link). 


***

## `r viostr`


`r if(length(vio) == 0) contactstr`

`r if(nrow(dg1) > 0) paste0(l1a, "**", nrow(dg), "**", l1b, "**", nrow(dg1), "**", l1c, "**", ee, "**", l1d) `

`r if(nrow(dg1) > 0) paste(l2) `



```{r, out.width="100%"}
colourCount = length(unique(dg1$CHEMICAL__))
getPalette = colorRampPalette(RColorBrewer::brewer.pal(9, "Set1"))

if(nrow(dg1) > 0){
  p <- mutate(dg1, CHEMICAL__ = stringr::str_wrap(CHEMICAL__, 15,1,1)) %>% 
    ggplot(aes(fct_reorder(CHEMICAL__, prop_mcl), 
                       prop_mcl, 
                       fill = CHEMICAL__,
                       text = paste("Chemical:", CHEMICAL__, "<br>",
                                    "Exceedance:", round(prop_mcl, 2), "%", "<br>",
                                    "Average Result:", round(mean_finding, 2), RPT_UNIT, "<br>",
                                    "MCL:", MCL, RPT_UNIT, "<br>",
                                    "XMOD:", XMOD),
                       group = 1)) +
    geom_col() +
    scale_y_continuous(breaks = c(0,25,50,75,100),
                       labels = function(x) paste0(x, "%")) +
    coord_cartesian(ylim = c(0, 110)) +
    labs(x = "Chemical", y = "Percent MCL Exceedance (%)", fill = "% Exceedance",
         #title = "How Clean is my Water?",
         subtitle = "Values less than 100% are safe.") +
    geom_hline(yintercept = 100, linetype = "dashed", color = "black") +
    #annotate("text", x = nrow(dg1)/3, y = 90, angle = 90, color = "red",
    #         label = "MCL Threshold") + 
    #coord_flip() +
    #scale_fill_viridis_d() +
    #scale_fill_brewer(palette = "Set2") +
    scale_fill_manual(values = getPalette(colourCount)) + 
    theme_minimal() +
    theme(panel.grid.minor = element_blank(),
          axis.text.x = element_blank(),
          panel.grid.major.x = element_blank()) +
    guides(fill = FALSE)
  
  ggplotly(p, tooltip = "text") %>% 
    config(modeBarButtonsToRemove = buttons_to_remove,
           displaylogo = FALSE)
}
```

`r if(nrow(dg1) > 0 & nrow(dg2) > 0) paste0("**", nrow(dg2), "**", l7)`

`r if(nrow(wqi) > 0) paste0("**", nrow(wqi), l8)`

***  

## Explore/download data {#table}

Explore your water quality data in the interactive table below, or download as an Excel or CSV file.  

```{r}
dg %>% 
  select(CHEMICAL__, mean_finding, MCL, RPT_UNIT, XMOD) %>% 
  mutate(mean_finding = round(mean_finding, 2)) %>% 
  datatable(., 
            colnames = c("CHEMICAL", "SAMPLE_MEAN","MCL","UNIT", "XMOD"),
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('excel', "csv"),
                           pageLength = 25))
```

*** 

<!-- `r if(nrow(dg1) > 0 & nrow(dg2) > 0) paste0("**", nrow(dg2), "**", l3, paste(dg2$CHEMICAL__, collapse = ", "), "." , l4) ` -->

<!-- `r if(nrow(dg1) == 0 & nrow(dg2) > 0) paste0(l5, "<br><br>", l6, paste(dg2$CHEMICAL__, collapse = ", "), ".") ` -->

<!-- `r if(nrow(wqi) > 0) paste0(l6a, nrow(wqi), l6b, "<br><br>", paste(wqi$CHEMICAL__, collapse = ", "), ".")` -->





<!-- ## Actions taken to address MCL exceedances _[in progress]_  -->
<!-- ## r if(nrow(violations) > 0) paste('Actions taken to assess violations') -->

<!-- When a measured contaminant exceeds the MCL, a set of regulatory actions is taken to improve water quality. All regulatory actions taken during the period of this report are shown below:   -->

<!-- Table or text summarizing this.   -->



<!-- ***   -->




<!-- ## How does my water compare to county and statewide averages? -->


<!-- ***   -->


<!-- ## My water quality over time. -->

<!-- Only showing this year's water quality data. What about the past 5 years? -->

<!-- ***   -->



## About

**`r params$nam`**, located in **`r paste0(params$city, ' (', params$county, ' CO.)')`**:   

`r paste0(' ', fontawesome::fa("users", fill = "#8105D8"))` services **`r tsc`** connections to serve a total population of **`r pop`** individuals.  

`r paste0(' ', fontawesome::fa("tint", fill = "#2B76CC"))` has a primary water source type of **`r wst`**.  

***  

### Contact {#contact-link}

> `r paste0(params$nam, "<br>", fontawesome::fa("map-marker", fill = "red"), "   ", cd$WS_ADDRESS, "<br>", " ", fontawesome::fa("phone", fill = "blue"), "   ", cd$WS_PHONE)`  

> `r paste0("Health Agency: ", cd$HEALTH_DISTRICT, "<br>", fontawesome::fa("map-marker", fill = "red"), "   ", cd$HD_ADDRESS, "<br>", " ", fontawesome::fa("phone", fill = "blue"), "   ", cd$HD_PHONE, "<br>", " ", fontawesome::fa("paper-plane", fill = "green"), "   ", cd$HD_EMAIL)` 

```{r, out.width="100%", out.height="300px"}
if(nrow(my_water_system) > 0 ){
  mapview(my_water_system, legend = FALSE, layer.name = params$nam)
}
```

***  

### Disclaimer

This Consumer Confidence Report was automatically generated, and hence, the data herein may be incomplete or inaccurate. The authors claim no liability or responsibility for data quality, and this data product falls under the [MIT License](https://github.com/caccr/cawdc_2019/LICENSE). This data represents the average result of all post-treatment samples from the period from `r paste0(paste0(lubridate::year(Sys.Date()), '-01-01'), ' to ', Sys.Date())`.  

**For questions about your local water quality, [contact](#contact-link) your water system.**    

***

### FAQ {#vio-link}

To view frequently asked questions, [visit the FAQ](https://caccr.github.io/faq/).  


